---
title: "Class11 Sec6"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## GitHub Documents

This is an R Markdown format used for publishing markdown documents to GitHub. When you click the **Knit** button all R code chunks are run and a markdown file (.md) suitable for publishing to GitHub is generated.

## Including Code

You can include R code in the document as follows:

```{r cars}
library("bio3d")
library("XML")
library("RCurl")
aa <- get.seq("1ake_A")

# Blast or hmmer search
b <- hmmer(aa)

# Plot a summary of search results
hits <- plot(b)

head(hits$pdb.id)

```

## Including Plots

You can also embed plots, for example:

```{r }
# Fetch PDBs
files <- get.pdb(hits$pdb.id, path = "pdbs", split = TRUE, gzip =
TRUE)
# Align structures
pdbs <- pdbaln(files)
# Vector containing PDB codes
ids <- basename.pdb(pdbs$id)
# Draw schematic alignment
plot(pdbs, labels=ids)
```

6.2 Sequence conversation analysis
```{r}
#Calculate sequence conservation
cons <- conserv(pdbs, method="entropy22")
#SSE annotations
sse <- pdbs2sse(pdbs, ind=1, rm.gaps=FALSE)
# Plot conservation per residue
plotb3(cons, sse=sse, ylab="Sequence entropy")
```

6.3 Annotate collected PDB structures
```{r}
anno <- pdb.annotate(ids)
print(unique(anno$source))
```

